Eval expressions

### 2021-01-28 analysis/expressions.Rmd
fix variable names

canonic_expr_str <- function(exp, with.names = FALSE) {
    ast <- NA
    try(ast <- parse(text = exp)[[1]], silent = TRUE)
    # some expr_resolved have been truncated so we mark them as FALSE (even though they could be true)
    if (is.symbol(ast) || is.language(ast) || length(ast) > 1 || !is.na(ast)) {
        return(canonic_expr(ast, with.names))
    }
    else {
        return("NORMALIZATION ERROR")
    }
}
```

@@

res_exprs <- res_exprs %>% mutate(expr_canonic = map_chr(expr_resolved, canonic_expr_str))

res_exprs <- res_exprs %>% mutate(expr_canonic_names = map_chr(expr_resolved, canonic_expr_str), with.names = TRUE)

>>>>

canonic_expr_str <- function(exp, with.names = FALSE) {
    ast <- NA
    try(ast <- parse(text = exp)[[1]], silent = TRUE)
    # some expr_resolved have been truncated so we mark them as FALSE (even though they could be true)
    if (is.symbol(ast) || is.language(ast) || length(ast) > 1 || !is.na(ast)) {
        return(canonic_expr(ast, with.names))
    }
    else {
        return("NORMALIZATION ERROR")
    }
}

canonic_expr_str2 <- function(exp, with.names = FALSE) {
    ast <- NA
    try(ast <- parse(text = exp)[[1]], silent = TRUE)
  return("")
}
```

@@

res_exprs <- res_exprs_uniq %>% mutate(expr_canonic = map_chr(expr_resolved, canonic_expr_str))

# res_exprs <- res_exprs %>% mutate(expr_canonic_names = map_chr(expr_resolved, canonic_expr_str), with.names = TRUE)
